Intro Seminar

### 2017-03-01 doc/seminar2017.Rmd
Graphs for my introductory seminar slides

---
title: "**Urinary Vitamin D Binding Protein as a Potential Biomarker for Nephropathy in Patients at risk for Type 2 Diabetes**: The Prospective Metabolism and Islet Cell Evaluation (PROMISE) cohort study."
author: "Wang WZN, Cole DEC, Johnston LW, Wong BYL, Fu L, Retnakaran R, Harris SB, Zinman B, Hanley AJ"
output: word_document:
          fig_caption: yes
          reference_docx: wordStyle.docx
---

@@

```{r dsSetup}
ds <- project_data

dsBase <- ds %>% 
  dplyr::filter(fVN == "Baseline")

dsComplete <- ds %>% 
  dplyr::group_by(SID) %>%
  dplyr::filter(n() == 3) %>%
  dplyr::ungroup()
```

```{r captionSetup}
## Include captions below using `captioner` package
figNums <- captioner::captioner(prefix = 'Figure')
supFigNums <- captioner::captioner(prefix = 'Supplementary Figure')
tabNums <- captioner::captioner(prefix = 'Table')
supTabNums <- captioner::captioner(prefix = 'Supplementary Table')
```

@@

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("fVN"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR")) %>% 
  pander::pander()
```

>>>>

---
title: "Intro Seminar"
author: "Windy Wang"
date: "March 1, 2017"
output: html_document
---

@@

```{r dsSetup}
ds <- project_data
# 
# dsBase <- ds %>% 
#   dplyr::filter(fVN == "Baseline")
# 
# dsComplete <- ds %>% 
#   dplyr::group_by(SID) %>%
#   dplyr::filter(n() == 3) %>%
#   dplyr::ungroup()
```

@@

subCharTable <- tableone::CreateTableOne(
  vars = c("Age",
           "Sex",
           "Ethnicity",
           "BMI",
           "Waist",
           "eGFR",
           "ACR",
           "UrineCreatinine",
           "UrineMicroalbumin",
           "UrinaryCalcium",
           "UDBP",
           "Creatinine",
           "VitaminD",
           "PTH",
           "ALT",
           "Systolic",
           "Diastolic",
           "MeanArtPressure",
           "Glucose0",
           "Glucose120",
           "dmStatus",
           "SmokeCigs"),
  strata = c("UDBPStatus"),
  data = ds,
  factorVars = c("Sex", "SmokeCigs")
) %>% 
  print(nonnormal = c("Glucose0",
                      "Glucose120",
                      "ALT",
                      "UDBP",
                      "ACR")) %>% 
  knitr::kable()
```
